Presentation Title

### 2017-08-15 thesis/chapters/ch1-intro.tex
Update code URL in README
Add payment channel centralisation, etc.

Sadly, as traditional blockchain systems began to gain popularity,
their limitations also became apparent.
Bitcoin has the infamous 7 transactions per second upper bound~\cite{vukolic2015quest}.
This is due to the fact that blocks are fixed to 1 MB,
and are only generated on average every 10 minutes.
Since every Bitcoin transaction is at least 250 bytes, it computes to about 7 transactions per second.
Due to this limitation, it is not uncommon to see a long backlog of about 20,000 transactions\footnote{\url{https://blockchain.info/unconfirmed-transactions/}}.
A few months ago the backlog even reached 100,000, which meant new transactions would take at least 11 hours to be written to the blockchain~\cite{bitcoinbacklog}.
This issue has plagued the Bitcoin community for some time and is the root cause for the block size debate, which some calls it a civil war~\cite{bitcoincivilwar}.
Parties that are for the increase in block size argue that a larger block would improve the transaction rate.
Parties against it argue that it would make mining more centralised because blocks take longer to propagate through the network.
It also requires a hard (non-backwards compatible) fork,
which risks consensus failure and devaluation.
A recent empirical study by Croman et el.~\cite{croman2016scaling} has shown that increasing the block size or the block interval may help.
But given the bandwidth and latency constraints of today's network,
it is not possible to have more than 758 transactions per second if messages need to be propagated timely to 90\% of the nodes.
To achieve transaction rates higher than that, it will lead to unfairness for nodes that do not have a good network connection.
Thus fundamental changes are necessary to run at the scale of centralised payment processors such as Visa,
which is in the order of tens of thousands transactions per second~\cite{visa}.

@@

Our main contributions are the following.
\begin{itemize}
    \item We formally introduce a blockchain system---\textsc{Checo}.
        It uses individual hash chains and checkpoints on every node to achieve
        horizontally scalable for the first time.
    \item We formally analyse \textsc{Checo} to ensure correctness as defined in our architecture.
    \item We provide an implementation and then experiment with up to 1200 nodes,
        our results show strong evidence of horizontal scalability.
\end{itemize}

>>>>

Sadly, as traditional blockchain systems began to gain popularity,
their limitations also became apparent.
Bitcoin has the infamous 7 transactions per second upper bound~\cite{vukolic2015quest}.
This is due to the fact that blocks are fixed to 1 MB,
and are only generated on average every 10 minutes.
Since every Bitcoin transaction is at least 250 bytes, it computes to about 7 transactions per second.
Due to this limitation, it is not uncommon to see a long backlog of about 20,000 transactions\footnote{\url{https://blockchain.info/unconfirmed-transactions/}}.
A few months ago the backlog even reached 100,000, which meant new transactions would take at least 11 hours to be written to the blockchain~\cite{bitcoinbacklog}.
This issue has plagued the Bitcoin community for some time and is the root cause for the block size debate, which some calls it a civil war~\cite{bitcoincivilwar}.
Parties that are for the increase in block size argue that a larger block would improve the transaction rate.
Parties against it argue that it would make mining more centralised because blocks take longer to propagate through the network.
It also requires a hard (non-backwards compatible) fork,
which risks consensus failure and devaluation.
A recent empirical study by Croman et el.~\cite{croman2016scaling} has shown that increasing the block size or the block interval may help.
But given the bandwidth and latency constraints of today's network,
it is not possible to have more than 27 transactions per second.
To achieve transaction rates higher than that, it will lead to unfairness for nodes that do not have a good network connection.
Thus fundamental changes are necessary to run at the scale of centralised payment processors such as Visa,
which is in the order of tens of thousands transactions per second~\cite{visa}.

@@

Our main contributions are the following.
\begin{itemize}
    \item We formally introduce a blockchain system---\textsc{Checo}.
        It uses individual hash chains and checkpoints on every node to achieve
        horizontally scalable in the general case for the first time.
    \item We formally analyse \textsc{Checo} to ensure correctness as defined in our architecture.
    \item We provide an implementation and then experiment with up to 1200 nodes,
        our results show strong evidence of horizontal scalability.
\end{itemize}

### 2017-08-15 thesis/chapters/ch2-problem.tex
Give paper a structure
Add payment channel centralisation, etc.

The advantage of this approach is that it can be used in a large network.
In fact, prior to Bitcoin, there was no internet-scale consensus protocol.
Bitcoin is also fault-tolerant because attackers can not out pace honest users in finding new blocks unless they have a majority of the hash power.
As long as the majority is honest and reasonable measures are taken to prevent the selfish mining attack~\cite{eyal2014majority}.
The disadvantage, however, is that transactions are never in consensus with a probability of 1---no consensus finality.
Hence double spending is possible for transactions that do not have a large number of confirmations.
Furthermore, as we mentioned in the Introduction,
the performance is limited due to the fact that blocks are of fixed size and are generated at fixed intervals.
Thus early blockchain systems do not achieve horizontal scalability.

@@

On the other hand, off-chain transactions also suffer from the problem of Bitcoin.
Namely, proof-of-work consumes an unreasonable amount of power.
Further, payment channels complicate user experience.
As we mentioned earlier, each node must deposit some Bitcoins into a multi-signature account.
The users must pick a suitable amount.
If the deposit is too low it would not allow large transactions.
If the deposit is too high the user is locked out of much of its Bitcoins for use outside of the channel.
In addition, the user must proactively check whether the counterparty has broadcasted an old channel state so that the user does not lose Bitcoins.
Payment channel, in theory, solves the scalability problem of early blockchain systems,
but to the best of our knowledge, its exact scalability characteristics are not investigated.

@@

We saw in~\Cref{sec:taxonomy} that the majority of the systems cannot achieve horizontal scalability.
That is, by adding new nodes into the network, the global transaction rate should increase proportionally.
To the best of our knowledge, only two systems---Elastico~\cite{luu2016elastico} and OmniLedger~\cite{kokoris2017omniledger}---has experimentally demonstrated horizontal scalability.
However, these techniques rely on sharding, thus the performance highly depends on transaction characteristics and the shard size parameter because inter-shard transactions are slow.
Furthermore, all the systems described in~\Cref{sec:taxonomy} are complete blockchain systems designed for a concrete application.
We wish to design a blockchain consensus protocol that can be used in many applications.
For example recording uploads and downloads between peers in Tribler~\cite{pouwelse2008tribler, multichain} and decentralised market\footnote{\url{https://github.com/Tribler/tribler/blob/devel/Tribler/community/tradechain/__init__.py}}.
Hence our research question is the following.
\begin{displayquote}
\emph{Is it possible to design a blockchain consensus protocol that is fault-tolerant, scalable and can reach global consensus?}
\end{displayquote}

>>>>

The advantage of this approach is that it can be used in a large network.
In fact, prior to Bitcoin, there was no internet-scale consensus protocol.
Bitcoin is also fault-tolerant because attackers can not out pace honest users in finding new blocks unless they have a majority of the hash power.
As long as the majority is honest and reasonable measures are taken to prevent the selfish mining attack~\cite{eyal2014majority}.
The disadvantage, however, is that transactions are never in consensus with a probability of 1---no consensus finality.
Hence double spending is possible for transactions that do not have a large number of confirmations.
Furthermore, as we mentioned in the~\Cref{ch:intro},
the performance is limited due to the fact that blocks are of fixed size and are generated at fixed intervals.
Thus early blockchain systems do not achieve horizontal scalability.

@@

On the other hand, payment channel complicates user experience and leads to centralisation.
As we mentioned earlier, each node must deposit some Bitcoins into a multi-signature account.
The users must pick a suitable amount.
If the deposit is too low it would not allow large transactions.
If the deposit is too high the user is locked out of much of its Bitcoins for use outside of the channel.
In addition, the user must proactively check whether the counterparty has broadcasted an old channel state so that the user does not lose Bitcoins.
Furthermore, creating channels with sufficient balance and also keeping it online to act as a router is expensive.
A casual user is not capable of such tasks, thus it leads to centralisation.
Payment channels, in theory, solve the scalability problem of early blockchain systems,
but to the best of our knowledge, its exact scalability characteristics are not investigated.

@@

We saw in~\Cref{sec:taxonomy} that the majority of the systems cannot achieve horizontal scalability.
To the best of our knowledge, only two systems---Elastico~\cite{luu2016elastico} and OmniLedger~\cite{kokoris2017omniledger}---has experimentally demonstrated horizontal scalability.
However, these techniques rely on sharding, thus the performance highly depends on transaction characteristics and the shard size parameter because inter-shard transactions are slow.
Furthermore, all the systems described in~\Cref{sec:taxonomy} are complete blockchain systems designed for a concrete application.
We wish to design a blockchain consensus protocol that can be used in many applications.
For example recording uploads and downloads between peers in Tribler~\cite{pouwelse2008tribler, multichain} and decentralised market\footnote{\url{https://github.com/Tribler/tribler/blob/devel/Tribler/community/tradechain/__init__.py}}.
Hence our research question is the following.
\begin{displayquote}
\emph{Is it possible to design a blockchain consensus protocol that is fault-tolerant, scalable and can reach global consensus?}
\end{displayquote}

### 2017-08-15 thesis/chapters/ch3-model.tex
Improve abstract
Add payment channel centralisation, etc.

If there exist a tuple $\langle c_{u,a}, c_{u, b} \rangle$ for a TX block $t_{u, i}$,
where 
$$a = \argmin_{k, k < i, \texttt{typeof}(b_{u,k}) = \gamma}(i - k)$$
$$b = \argmin_{k, k > i, \texttt{typeof}(b_{u,k}) = \gamma}(k - i),$$
then $\langle c_{u,a}, c_{u, b} \rangle$ is the enclosure of $t_{u, i}$.
Intuitively, that is the two closest CP blocks that surround $t_{u, i}$.
Note that $c_{u, a}$ is the more recent CP block.
Also, some TX blocks may not have any enclosure, then its enclosure is $\bot$.
Agreed enclosure is the same as enclosure with an extra constraint where the CP blocks must be in some consensus result $\C_r$.

@@

Before describing the protocol in detail,
we take a brief detour to give background on the ACS algorithm as it is the primary building block.
Then we move on to describe the two phases of our consensus protocol---bootstrap phase and consensus phase.

@@

Upon receiving $\C_{r + 1}$ and at least $n - f$ valid signatures by some node $u$, $u$ performs two tasks.
First, it creates a new CP block using $\textsf{new\_cp}(\C_{r + 1}, r + 1)$ (\Cref{alg:new-cp}).
Second, it computes the new facilitators using $\textsf{get\_facilitator}(\C_{r + 1}, n)$ (\Cref{alg:facilitator}),
and updates its facilitator set to the result.
This concludes the consensus phase and brings us back to the state at the beginning of the consensus phase,
so a new round can be started.

\begin{algorithm}
\caption{Function $\textsf{new\_cp}(\C_r, r)$ runs in the context of the caller $u$.
It creates a new CP block and appends it to $u$'s chain.}
\label{alg:new-cp}
\begin{algorithmic}
\State $h \gets |B_u|$
\State $c_{u, h} \gets \langle \textsf{H}(b_{u, h-1}), h, \textsf{H}(\C_r), r, sig_u \rangle$
\State $B_u \gets B_u \cup c_{u, h}$
\end{algorithmic}
\end{algorithm}

@@

We make two remarks.
First, just like the TX protocol, we do not block at any part of the protocol.
Second, suppose some $F_{v, j}$ validates $t_{u, i}$, then that does not imply that $t_{u, i}$ only has one pair $t_{v, j}$.
Our validity requirement only requires that there is only one $t_{v, j}$ in the correct consensus round.
The counterparty may create any number of fake pairs in later consensus rounds.
But these fake pairs only pollutes the chain of $v$ and can never be validated because the round is incorrect.

@@

We offer two approaches to do total fork detection.
First and the easiest solution is to simply ask for the complete chain of the counterparty.
The verifier can be sure that there are no forks if the following holds.
\begin{enumerate}
    \item The hash pointers are correct.
    \item All the CP blocks are in consensus.
    \item The TX of interest is in the chian.
\end{enumerate}
We use this approach in our prior work on Implicit Consensus~\cite{implicitconsensus}.
Nodes employ caching to minimise communication costs, we call this effect spontaneous sharding.

The second approach is probabilistic but with only a constant communication overhead over our current design.
For a node, observe that if all of its agreed fragments has a transaction with an honest node,
then the complete chain is effectively validated in a distributed manner.
The only way for an attacker to make a fork is to make sure that the agreed fragment containing the fork has no transactions with honest nodes.
Such malicious behaviour is prevented probabilistically using a challenge-response protocol as follows.
Suppose node $A$ wish to make a transaction with node $B$.
$A$ first sends a challenge to $B$ asking it to prove that it holds a valid agreed fragment between some consensus round specified by $A$.
If $B$ provides a correct proof, then they run the transaction protocol as usual.
If $B$ provides an invalid proof or refuses to respond,
then $A$ would refuse to make the transaction.

>>>>

If there exist a tuple $\langle c_{u,a}, c_{u, b} \rangle$ for a TX block $t_{u, i}$,
where 
$$a = \argmin_{k, k < i, \textsf{typeof}(b_{u,k}) = \gamma}(i - k)$$
$$b = \argmin_{k, k > i, \textsf{typeof}(b_{u,k}) = \gamma}(k - i),$$
then $\langle c_{u,a}, c_{u, b} \rangle$ is the enclosure of $t_{u, i}$.
Intuitively, that is the two closest CP blocks that surround $t_{u, i}$.
Note that $c_{u, a}$ is the more recent CP block.
Also, some TX blocks may not have any enclosure, then its enclosure is $\bot$.
Agreed enclosure is the same as enclosure with an extra constraint where the CP blocks must be in some consensus result $\C_r$.

@@

Before describing the protocol in detail,
we take a brief detour to give background on the ACS protocol as it is the primary building block.
Then we move on to describe the two phases of our consensus protocol---bootstrap phase and consensus phase.

@@

Upon receiving $\C_{r + 1}$ and at least $n - f$ valid signatures by some node $u$, $u$ performs two tasks.
First, it creates a new CP block using $\textsf{new\_cp}(\C_{r + 1})$ (\Cref{alg:new-cp}).
Second, it computes the new facilitators using $\textsf{get\_facilitator}(\C_{r + 1}, n)$ (\Cref{alg:facilitator}),
and updates its facilitator set to the result.
This concludes the consensus phase and brings us back to the state at the beginning of the consensus phase,
so a new round can be started.

\begin{algorithm}
\caption{Function $\textsf{new\_cp}(\C_r)$ runs in the context of the caller $u$.
It creates a new CP block and appends it to $u$'s chain.}
\label{alg:new-cp}
\begin{algorithmic}
\State $\langle r, \_ \rangle \gets \C_r$
\State $h \gets |B_u|$
\State $c_{u, h} \gets \langle \textsf{H}(b_{u, h-1}), h, \textsf{H}(\C_r), r, sig_u \rangle$
\State $B_u \gets B_u \cup c_{u, h}$
\end{algorithmic}
\end{algorithm}

@@

We make two remarks.
First, just like the TX protocol, we do not block any part of the protocol.
Second, suppose some $F_{v, j}$ validates $t_{u, i}$, then that does not imply that $t_{u, i}$ only has one pair $t_{v, j}$.
Our validity requirement only requires that there is only one $t_{v, j}$ in the correct consensus round.
The counterparty may create any number of fake pairs in later consensus rounds.
But these fake pairs only pollutes the chain of $v$ and can never be validated because the round is incorrect.

@@

We offer two approaches to do total fork detection.
First and the easiest solution is to simply ask for the complete chain of the counterparty.
The verifier can be sure that there are no forks if the following holds.
\begin{enumerate}
    \item The hash pointers are correct.
    \item All the CP blocks are in consensus.
    \item The TX of interest is in the chain.
\end{enumerate}
We use this approach in our prior work on Implicit Consensus~\cite{implicitconsensus}.
Nodes employ caching to minimise communication costs, we call this effect spontaneous sharding.

The second approach is probabilistic but with only a constant communication overhead over our current design.
For a node, observe that if all of its agreed fragments has a transaction with an honest node,
then the complete chain is effectively validated in a distributed manner.
The only way for an attacker to make a fork is to make sure that the agreed fragment containing the fork has no transactions with honest nodes.
Such malicious behaviour is prevented probabilistically using a challenge-response protocol as follows.
Suppose node $A$ wish to make a transaction with node $B$.
$A$ first sends a challenge to $B$ asking it to prove that it holds a valid agreed fragment between some consensus round specified by $A$.
If $B$ provides a correct and timely response, then they run the transaction protocol as usual.
Otherwise, $A$ would refuse to make the transaction.

### 2017-08-15 thesis/formalities/abstract.tex
Add payment channel centralisation, etc.

\begin{abstract}
% what's the problem?
Blockchain systems have the potential to decentralise many traditionally centralised system.
However, scalability remains a key challenge.
Without a horizontally scalable solution, blockchain system remain unsuitable for ubiquitous use.
% what's the solution?
We design a novel blockchain system called \textsc{Checo}.
Each node in our system maintain individual hash chains,
which only stores transactions that the node is involved in.
Consensus is reached on special blocks called checkpoint blocks rather than on all the transactions.
Checkpoint blocks are effectively a hash pointer to the individual hash chains,
thus a single checkpoint block may represent a large set of transaction blocks.
The consensus protocol does not imply transaction validity.
Hence we include a validation protocol which allows nodes to verify that transactions are correctly recorded,
which indirectly achieves consensus on transactions.
% how good is the solution?
We implement a prototype and evaluate it experimentally.
Our results show strong indication of horizontal scalability even in the worst case,
where every transaction is made with a randomly selected node.
For 1200 nodes, we were able to perform almost 5000 transactions per second,
orders of magnitude higher than the 7 transaction per second limit of Bitcoin.
\end{abstract}

>>>>

\begin{abstract}
% what's the problem?
Blockchain systems have the potential to decentralise many traditionally centralised systems.
However, scalability remains a key challenge.
Without a horizontally scalable solution, blockchain systems remain unsuitable for ubiquitous use.
% what's the solution?
We design a novel blockchain system called \textsc{Checo}.
Each node in our system maintains individual hash chains,
which only stores transactions that the node is involved in.
A consensus is reached on special blocks called checkpoint blocks rather than on all the transactions.
Checkpoint blocks are effectively a hash pointer to the individual hash chains,
thus a single checkpoint block may represent a large set of transaction blocks.
The consensus protocol does not imply transaction validity.
Hence we include a validation protocol which allows nodes to verify that transactions are correctly recorded,
which indirectly achieves consensus on transactions.
% how good is the solution?
We implement a prototype and evaluate it experimentally.
Our results show a strong indication of horizontal scalability even in the worst case,
where every transaction is made with a randomly selected node.
For 1200 nodes, we were able to perform almost 5000 transactions per second,
orders of magnitude higher than the 7 transactions per second limit of Bitcoin.
\end{abstract}
